\documentclass[11pt]{article}

\newcommand{\ME}{\textsc{MutationExplorer}}

\begin{document}

\title{\ME - a server for mutating proteins and visualising the energetic effect in 3D}
\author{ Michelle Kampfrath*, Nikola Ristic*,  Johanna Tiemann, \\Peter W. Hildebrand, Daniel Wiegreffe, René Staritzbichler}
\date{\today}
\maketitle

\noindent
* authors contributed equally.
Correspondence: René, Daniel

\begin{abstract}
 \ME
\end{abstract}

\section*{Introduction}

Role of mutations
\begin{itemize}
\item driving force of evolution
\item cause of disease, foremost cancer
\end{itemize}


\noindent
Sequencing:
\begin{itemize}
\item Sequence versus structure
\item NGS
\end{itemize}


\noindent
Protein conformations: 
\begin{itemize}
\item PDB
\item alphaFold (makes this tool very universal!)
\item user provided: multitude of modelling/simulation techniques
\end{itemize}


\clearpage

\noindent
Server:
\begin{itemize}
\item Systematic evaluation (upload sequencing data(?) / mutation data / alignment)
\item Manual try and see (GUI)
\end{itemize}


\noindent
Applications:
\begin{itemize}
\item (De)-stabilising protein interfaces
\item (De)-stabilising protein conformations
\item Evaluating sequencing data
\item Understanding alignments
\item Homology modelling
\end{itemize}


\noindent
Analysis types / coloring schemes:
\begin{itemize}
\item Per residue energies
\item Energy difference from mutants to wildtype
\item Sequence conservation / NGS
\item Profiles: hydrophobicity and other scales
\item Differences of profiles from mutant to wildtype
\end{itemize}


\noindent
Interface with AlignMe.
Integrate into any other server. 
Explanations in FAQs.

\noindent
Visualisation builds on Mol* and MDsrv. \\
Yet another server on our farm: cite: SmoothT, ProteinPrompt, MDCiao, Voronoia, ...

\section*{Methods and description}

\subsection*{Rosetta}


\begin{itemize}
\item Basic concepts: knowledge based potentials
\item Minimization
\item Design
\item Energy breakdown
\end{itemize}

\subsection*{Mol* viewer}

\begin{itemize}
\item successor of NGL (developed in our lab)
\item \ME ~builds on developments in MDsrv
\item direct collaboration with Mol*
\item 'dual view': interactive windows: alignment and structure
\end{itemize}

\subsection*{Webserver / Usage}

\begin{itemize}
\item from AlignMe or other alignment server
\item GUI
\end{itemize}

\subsection*{Examples}

\begin{itemize}
\item (de)-stabilising protein interfaces
\end{itemize}


\subsection*{Interface}

\begin{itemize}
\item Tool for identifying driver cancer mutations
\end{itemize}


\section*{Conclusions}

\section*{Availability}
\begin{itemize}
\item \ME
\item MDsrv / Mol*
\end{itemize}

\section*{Acknowledgements}
The testers.

\section*{Funding}

\begin{itemize}
\item 
\end{itemize}

\clearpage

\section*{FAQ}

\begin{itemize}
\item Is it possible to mutate peptides?
\item Is it possible to mutate transmembrane proteins?
\item What about nonstandard AA, lipids, ions?
\item How to mutate a mutant? How to perform multiple rounds of mutations? 
\item How to link an alignment server for 3D visualisation to \ME
\end{itemize}





\end{document}
